A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-31 writeup/paper.tex
small changes

There are several complicating factors when trying to take a census of workers on MTurk.  The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.  Posting a simple survey to have workers self-report this information may be inadequate, since (a) many worker may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.

Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying. We ask workers what languages they speak and what country they live in, and validate their claims by measuring their ability to correctly translate words and by geolocating them.  To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.  These tasks each consist of translating 10 foreign words into English.  Two of the 10 words have known translations, allowing us to validate the the workers' translations are accurate.  We construct bilingual dictionaries with up to 10,000 entries, with the majority of entries being new.

@@

We calculate the quality of translations on the level of individual assignments, individual workers, and languages.  We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
\begin{align}	
	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
\end{align}	
where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true. 
Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.

@@

Quality for a language is then given by
\begin{align}	
	\text{Quality}(l_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
\end{align}	
where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above.

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{figure*}
\footnotesize
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czechr Rpublic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&Southafrica (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We measured the average quality of workers who were in countries that plausibly speak a language, versus workers from countries that did not have large speaker populations of that language.  We used the Ethnologue \cite{ethnologue} to compile the list of countries where each language is spoken.  Table \ref{region-summary} compares the average translation quality of Turkers within the region of each language, and compares it to the quality of Turkers outside that region.

>>>>

There are several complicating factors when trying to take a census of workers on MTurk.  The workers' identities are anonymized, and Amazon provides no information about their countries of origin or their language abilities.  Posting a simple survey to have workers self-report this information may be inadequate, since (a) many workers may never see the survey, (b) many opt not to do one-off surveys since potential payment is low, and (c) validating the answers of respondents is not straightforward.

Our study establishes a methodology for determining the language demographics of anonymous crowd workers that is more robust than simple surveying. We ask workers what languages they speak and what country they live in, and validate their claims by measuring their ability to correctly translate words and by recording their geolocation.  To increase the visibility and the desirability of our tasks, we post 1,000 assignments in each of 119 languages.  These tasks each consist of translating 10 foreign words into English.  Two of the 10 words have known translations, allowing us to validate that the workers' translations are accurate.  We construct bilingual dictionaries with up to 10,000 entries, with the majority of entries being new.

@@

We calculate the quality of translations on the level of individual assignments and aggregated over languages and countries.  We define an assignment's quality as the proportion of controls that are correct in a given assignment, where correct means exactly correct or judged to be synonymous.
\begin{align}	
	\text{Quality}(a_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{\delta}(tr_{ij} \in \texttt{syns[$g_j$]})
\end{align}	
where $a_i$ is the $i^{th}$ assignment, $k_i$ is the number of controls in $a_i$, $tr_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $g_j$ is the gold standard translation of control word $j$, \texttt{syns[$g_j$]} is the set of words judged to be synonymous with $g_j$ and includes $g_j$, and $\mathbf{\delta}(x)$ is Kronecker's delta and takes value 1 when $x$ is true. 
Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.

@@

Quality for a language is then given by
\begin{align}	
	\text{Quality}(l_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
\end{align}	
where $l_i$ is the ith language, \texttt{assigns[$i$]} is the set of completed assignments for language $i$, and Quality($a$) is as above. Quality for a country is computed the same way.

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{figure*}
\footnotesize
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We measured the average quality of workers who were in countries that plausibly speak a language, versus workers from countries that did not have large speaker populations of that language.  We used the Ethnologue \cite{ethnologue} to compile the list of countries where each language is spoken.  Table \ref{region-summary} compares the average translation quality of assignments completed within the region of each language, and compares it to the quality of assignments completed outside that region.
